quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-17 paper-quollr.Rmd
Updated Linked plot projections

@@

proj_obj2[["cluster"]] <- factor(scurve_umap_scaled_select1$select_area,
                                 levels=c("deselected", "selected"))

projected_df <- proj_obj2$projected_df
model_df <- proj_obj2$model_df
axes <- proj_obj2$axes
circle <- proj_obj2$circle

projected_df <- projected_df |>
  dplyr::mutate(cluster = proj_obj2$cluster)

scurve_proj_umap_model1_selected1 <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "a2", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

scurve_proj_umap_model1_selected1_dp <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "a3", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

proj_obj2[["cluster"]] <- factor(scurve_umap_scaled_select2$select_area,
                                 levels=c("deselected", "selected"))

projected_df <- proj_obj2$projected_df
model_df <- proj_obj2$model_df
axes <- proj_obj2$axes
circle <- proj_obj2$circle

projected_df <- projected_df |>
  dplyr::mutate(cluster = proj_obj2$cluster)

scurve_proj_umap_model1_selected2 <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "b2", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

scurve_proj_umap_model1_selected2_dp <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "b3", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

>>>>

proj_obj2_cp <- get_projection(projection = projection, 
                            highd_data = scaled_scurve_data, 
                            model_highd = scaled_scurve_data_model, 
                            trimesh_data = tr_from_to_df_scurve, 
                            axis_param = list(limits = 0.6, 
                                              axis_scaled = 3,
                                              axis_pos_x = -0.4, 
                                              axis_pos_y = -0.4, 
                                              threshold = 0.05))

@@

proj_obj2_cp[["cluster"]] <- factor(scurve_umap_scaled_select1$select_area,
                                 levels=c("deselected", "selected"))

projected_df <- proj_obj2_cp$projected_df
model_df <- proj_obj2_cp$model_df
axes <- proj_obj2_cp$axes
circle <- proj_obj2_cp$circle

projected_df <- projected_df |>
  dplyr::mutate(cluster = proj_obj2_cp$cluster)

scurve_proj_umap_model1_selected1 <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.5,
        alpha = 0.3) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.5, 0.47)) +
        ylim(c(-0.5, 0.47)) +
  interior_annotation(label = "a2", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

scurve_proj_umap_model1_selected1_dp <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.5,
        alpha = 0.3) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.5, 0.47)) +
        ylim(c(-0.5, 0.47)) +
  interior_annotation(label = "a3", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

proj_obj2_cp[["cluster"]] <- factor(scurve_umap_scaled_select2$select_area,
                                 levels=c("deselected", "selected"))

projected_df <- proj_obj2_cp$projected_df
model_df <- proj_obj2_cp$model_df
axes <- proj_obj2_cp$axes
circle <- proj_obj2_cp$circle

projected_df <- projected_df |>
  dplyr::mutate(cluster = proj_obj2_cp$cluster)

scurve_proj_umap_model1_selected2 <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.5,
        alpha = 0.3) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.5, 0.47)) +
        ylim(c(-0.5, 0.47)) +
  interior_annotation(label = "b2", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

scurve_proj_umap_model1_selected2_dp <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.5,
        alpha = 0.3) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.5, 0.47)) +
        ylim(c(-0.5, 0.47)) +
  interior_annotation(label = "b3", cex = 3) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```
